Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})

### 2020-01-21 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

\begin{quote}
    \textit{Thanks for the opportunity to add more detail.  Additional model statistics have been included on lines ...}
\end{quote}

\textbf{
Line 162: The discussion and introduction seems to have been written by different people. The language used in the discussion is much more "fuzzy" than in the intro. I suggest re-wording much of the discussion to make it less wordy and repetitive and place the findings into a larger context.
}

Line 167: was this personal observation or speculation?

\begin{quote}
    \textit{Excellent question.  This was a personal observation. Details to that effect have been included on lines ...}
\end{quote}

@@

Line 169: Suggest simplifying this paragraph, its a long and convoluted way of saying that dose didn't matter.

\begin{quote}
    \textit{\textbf{EDIT HERE}}
\end{quote}

Line 174: Its not clear what this sentence is about, please re-word to clarify.

\begin{quote}
    \textit{Thanks for the suggestion.  We've reworded the sentence to make it clear that we are estimating numbers of flies killed to place it in the larger context of population management.  }
\end{quote}

Line 176: caught how and where?

\begin{quote}
    \textit{Excellent opportunity to clarify.  This was clarified later in the paragraph, but merits inclusion earlier.  The adults were caught on sticky traps.  The phrase has been updated on lines...}
\end{quote}

Line 180: how does this compare to the many flies that are in a typical onion field? I'm not understanding the value of your analysis. Please clarify and related this info to a larger context.

\begin{quote}
    \textit{Thanks for your question.  This directly relates to your inquiry about Figure 1 previously.  In this paragraph, we place mortality due to the attract and kill strategy in the context of population dynamics in a typical onion field through comparison of data from the population monitoring trial discussed previously.  }
\end{quote}

Line 187: Or they were attracted but didn't contact the spheres?

\begin{quote}
    \textit{Thanks for your inquiry.  In this case, the discussion is regarding the use of sticky cards.  The previous part of this phrase explains exactly that the kill part of the strategy with sticky cards was ineffective.  }
\end{quote}

Line 188: a bit of discussion on why you suspected that these would change attractiveness would be great.

\begin{quote}
    \textit{Excellent suggestion.  We've included more details about our rationale on lines ...}
\end{quote}

Figure 3: suggest removing the background.

\begin{quote}
    \textit{Thanks for the helpful suggestion.  We've removed the background to enhance visibility.  }
\end{quote}

Line 196: Feels repetitive, the previous sentence covered this.

\begin{quote}
    \textit{Thanks for the suggestion.  These are actually two different cases.  Resistant populations and organic growers may elect to use this strategy, but have the option to use other methods.  There are some cases where conventional pesticides to combat onion maggot have been banned or are in the process of becoming banned which would render them unavailable as a control option.  }
\end{quote}

Figure 4: light grey is difficult to see, suggest using bars instead of dots and lines.

\begin{quote}
    \textit{Excellent suggestion.  We've adjusted the color scheme in the figures to enhance readability.  }
\end{quote}

### 2020-01-21 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

The authors did a great job writing the manuscript.  The introduction, methods, and results were easy to understand.

\begin{quote}
    \textit{Thank you for reading the manuscript and providing constructive feedback.  We appreciate the suggestions and have endeavored to include them in the revised version.  }
\end{quote}

On lines 54 and 55 the authors state field trials were conducted from 2006 to 2008, but they did NOT describe if all experiments were repeated in 2006, 2007, and 2008.  The authors need to describe which experiments were conducted each year, how many times each experiment was replicated, and if the experiments were replicated in space and time.

\begin{quote}
    \textit{Thanks for the opportunity to clarify.  Details on the timing of trials are now included in at the beginning of each sub-section in the Material and Methods section on lines 60-61, 68-69, 73-75, 81-84, and 105-106.  In short, the trials were replicated in space and time.  }
\end{quote}

@@

The authors should add a few sentences describing the field sites (lines 54-56) cropping history (e.g. Where onions grown in previous years?) and the reason why the fields were chosen (e.g. did the fields have a previous history of onion maggot damage?).  If experiments were not replicated in space or time it should be noted in the Material and Methods.

\begin{quote}
    \textit{Thanks for mentioning this opportunity to elaborate.  Details on cropping history and reasoning behind field site choice have now been included on lines 55-58.  Information on how experiments were replicated in space and time is also included (see above).  }
\end{quote}

@@

In the discussion section the authors made no mention of using spinosad seed treatment as a management option in conventional and organic onion fields.  Why?? Spinosad (Regard) seed treatment is currently the primary management method for onion maggot in organic onions, and spinosad is an active ingredient in many conventional seed treatments.   Spinosad is an active ingredient in the FI500 seed treatment, and Regard alone often provides a similar level of protection compared to FI500.  Since FI500 resulted in lower maggot damage compared to all "attract and kill" tactics, why would someone recommend attract and kill with spinosad over spinosad seed treatment?   I strongly recommend the authors discuss the advantages, disadvantages, and compatibility of using spinosad seed treatment and spinosad attract & kill.

\begin{quote}
    \textit{This is an excellent point.  We've brought this up and elaborated more on exactly this point in the discussion as well as addressing the advantages and disadvantages of these strategies.  Thanks for the suggestion.  Additions can be found on lines 182-188.
    }
\end{quote}

The authors should discuss the implications of onion maggot developing resistance to spinosad using the attract and kill tactic.  e.g. Will the attract and kill tactic with spinosad lead to a higher likelihood of onion maggot developing resistance to spinosad?  This tactic targets egg laying adults, it only provides partial control, and it exposes multiple generations per year to spinosad?   These factors seem to favor resistance. This question is especially relevant as the most popular registered insecticide seed treatments contain spinosad and there are few alternatives in the marketplace.

\begin{quote}
    \textit{Also an excellent suggestion.  This is particularly important in systems where options are rapidly disappearing.  We've addressed this in more detail in the discussion on lines 186-188.  
    }
\end{quote}

@@

Line 65: Does this sentence belong to the next paragraph? move it there.

\begin{quote}
    \textit{Excellent suggestion.  This sentence does seem to be hanging there.  Rather than include it in the subsequent paragraph, we have opted to remove it alltogether.  }
\end{quote}

Line 66: be more specific.

\begin{quote}
    \textit{Thanks for the opportunity to elaborate.  We have included more details as to the timing and location of the trials throughout the methods section, specifically lines 60-61, 68-69, 73-75, 81-84, and 105-106. }
\end{quote}

@@

Line 68-69: This was already state above, seems redundant.

\begin{quote}
    \textit{Thanks for mentioning this.  We have removed the redundant statement.  }
\end{quote}

Line 71: More details are needed: how many reps/field, how many fields, how much distance between spheres, etc. Where in the field relative to the crop were spheres? What were they placed on and how high?

\begin{quote}
    \textit{Thanks for the opportunity to elaborate.  Details about reps, fields, distances, location, and height have been included on lines 72-75.
    }
\end{quote}

@@

Line 77: Which years was this experiment done? Throughout this section pls change to using SI units.

\begin{quote}
    \textit{Thanks for the suggestions.  Information on the timing of the experiment has been added to lines 81-82. Units have also been changed to SI.  Details have also been added regarding replications and field sites (lines 83-84).
    }
\end{quote}

@@

Line 91: was this based on a preliminary experiment?

\begin{quote}
    \textit{This was indeed based on previous work establishing the attractiveness of the spheres (Willett et al 2019). }
\end{quote}

Line 99: novel? How was it different from previously used ones?

\begin{quote}
    \textit{New but not novel.  It differed from previous formulations with the addition of the two extra components included below.  We have elaborated on the reasons for developing this on lines 103-104.   
    }
\end{quote}

@@

Line 104: was this true for previous experiments as well? If yes, please mention above.

\begin{quote}
    \textit{This was indeed true for previous experiments as well.  Thanks for the suggestion; these details have been included in the sections above as well.  }
\end{quote}

Line 108: which years?

\begin{quote}
    \textit{Great question.  This information has been included and elaborated upon in all methods sections on lines 60-61, 68-69, 73-75, 81-84, and 105-106. 
    }
\end{quote}

@@

Line 112: aren't these the same thing?

\begin{quote}
    \textit{Thanks for your question.  Yes and No.  While linear models and analysis of variance use the same underlying model structure, they have two different objectives and answer two different questions.  Linear models represent the relationship between independent and dependent variables.  Analysis of variance compares inter and intra-group variation to examine differences.  In our case, both approaches were used because we are interested both in modeling relationships and differences between groups.  }
\end{quote}

Line 113: I'd like to get more details about which factors you have used, fixed and random.

\begin{quote}
    \textit{Thanks for suggesting this inclusion.  We've listed the fixed and random factors used in the analysis on lines 118-120.
    }
\end{quote}

@@

Line 116: Why use both, why not just one or the other?

\begin{quote}
    \textit{Tukey HSD test generally is used to evaluate all pairwise comparisons.  Dunnett's test evaluates treatments versus controls.  In some cases we are only interested in comparisons versus controls (more powerful statistically as the correction for the family wise error rate is lower for less comparisons) while in others we are interested in more detailed comparisons.  }
\end{quote}

Line 117: Be more explicit about which model goes with what data. I'd like to see a list of dependent and independent variables and fixed and random effects.I suggest removing such a blanket statement and being more specific as I mentioned above.

\begin{quote}
    \textit{Thanks for the suggestion.  We've included more detail about the models and factors used for each datasets on lines 118-120.  In addition, the exact code to run the analysis with annotations and extensive documentation is publicly available on GitHub.  }
\end{quote}

@@

Line 143: Was this peak significantly different from the other times?

\begin{quote}
    \textit{Interesting question.  While we did not specifically test for this, peaks were either markedly reduced or noticeably absent for subsequent times in Figure 3.  }
\end{quote}

Line 154: This is compared to what?

\begin{quote}
    \textit{This comparison was made to spinosad spheres alone - specifics have been addded to lines 161-162.
    }
\end{quote}

@@

Line 157: be more specific about what treatments.

\begin{quote}
    \textit{In this case treatment was with the attract and kill strategies.  Details have been added to line 164.  }
\end{quote}

Line 159: are there any F-values or model results to go along with this?

\begin{quote}
    \textit{Thanks for the opportunity to add more detail.  Additional model statistics have been included on lines 166-167.}
\end{quote}

Line 162: The discussion and introduction seems to have been written by different people. The language used in the discussion is much more "fuzzy" than in the intro. I suggest re-wording much of the discussion to make it less wordy and repetitive and place the findings into a larger context.

\begin{quote}
    \textit{Thanks for your suggestions on improving the discussion.  Your comments have made the discussion more clear, direct, and readily accessible to the reader.  
    }
\end{quote}

@@

Line 167: was this personal observation or speculation?

\begin{quote}
    \textit{Excellent question.  This was a personal observation. Details to that effect have been included on line 175. 
    }
\end{quote}

Line 169: Suggest simplifying this paragraph, its a long and convoluted way of saying that dose didn't matter.

\begin{quote}
    \textit{Thanks for suggesting this.  Dose does matter - higher doses are more costly in terms of product used.  We've endeavored to highlight that higher doses do not seem to significantly augment control.  }
\end{quote}

@@

Line 187: Or they were attracted but didn't contact the spheres?

\begin{quote}
    \textit{Thanks for your inquiry.  In this case, the discussion is regarding the use of sticky cards.  The previous part of this phrase explains exactly that the kill part of the strategy with sticky cards was ineffective.  }
\end{quote}

Line 188: a bit of discussion on why you suspected that these would change attractiveness would be great.

\begin{quote}
    \textit{Excellent suggestion.  We've included more details about our rationale on lines 203-204. 
    }
\end{quote}

### 2020-01-23 manuscript/pest-management-science/main.tex
updated manuscript with co-author comments

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package. This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i. / 100 g seed]) and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate to stabilize the paraffin and improve performance. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.

@@

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-4.pdf}
\caption{Field damage of onions.  (A) Cumulative damage (number of dead onion plants) as a result of \textit{D. antiqua} larval feeding.  Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.  Different letters denote significant differences (p \textless 0.05).  (B) Field damage of onion in enclosed cages with differing spinosad sphere formulations.  Cumulative damage is number of dead plants as a result of \textit{D. antiqua} damage.  Points and error bars denote mean and 95\% confidence intervals respectively.  Different letters denote significant differences (p \textless 0.05). } 
\label{fig:figure4}
\end{figure}

@@

The viability of low doses could be particularly important in light of other uses of spinosad in onion fields.  Spinosad seed treatment is a widespread method used for control of onion maggot and common in other commercial seed treatments \citep{nault2006performance,nault2006onion, wilson2015evaluation}.  It is also present in the FI500 seed treatment and alone can offer comparable control \citep{nault2006performance,nault2006onion, wilson2015evaluation}.  These seed treatments are effective options of control of the larval stage; attract and kill methodologies using spinosad evaluated here target the mobile adults.  While exposure to an additional source of spinosad may foster development of resistance, strategies for preventing development of resistance could include rotating use of the active ingredient for the 'kill' part of the attract and kill strategy.

@@

While not as effective as insecticide controls, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.  Spinosad spheres do cause adult \textit{D. antiqua} mortality over extended field seasons.  In situations where immediate reduction in damage from \textit{D. antiqua} is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.  Additionally, this attract and kill approach could be used as a control option where conventional pesticides are no longer effective or available. This strategy could also hold promise as an additional mortality factor in longer term management to control \textit{D. antiqua} populations.

>>>>

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the Trigard OMC and Pro-Gro fungicide.  This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i. / 100 g seed]) and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate to stabilize the paraffin and improve performance. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.

@@

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-4.pdf}
\caption{Field damage of onions.  (A) Cumulative damage (number of dead onion plants) as a result of \textit{D. antiqua} larval feeding.  Solid points and error bars denote mean effects and 95\% confidence intevals respectively.  Different letters denote significant differences (p \textless 0.05).  (B) Field damage of onion in enclosed cages with differing spinosad sphere formulations.  Cumulative damage is number of dead plants as a result of \textit{D. antiqua} damage.  Points and error bars denote mean and 95\% confidence intervals respectively.  Different letters denote significant differences (p \textless 0.05). } 
\label{fig:figure4}
\end{figure}

@@

The viability of low doses could be particularly important in light of other uses of spinosad in onion fields.  Spinosad is widely used in seed treatments with many growers using the FarMore FI500 seed package which includes spinosad and can independently offer comparable control \citep{nault2006performance,nault2006onion, wilson2015evaluation}.  These seed treatments are effective options of control of the larval stage; attract and kill methodologies using spinosad evaluated here target the mobile adults.  While exposure to an additional source of spinosad may foster development of resistance, strategies for preventing development of resistance could include rotating use of the active ingredient for the 'kill' part of the attract and kill strategy.

@@

While not as effective as insecticide seed treatments, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.  Spinosad spheres do cause adult \textit{D. antiqua} mortality over extended field seasons.  In situations where immediate reduction in damage from \textit{D. antiqua} is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.  Additionally, this attract and kill approach could be used as a control option where conventional pesticides are no longer effective or available. This strategy could also hold promise as an additional mortality factor in longer term management to control \textit{D. antiqua} populations.
